---
title: "Lab 10 - Grading the professor, Pt. 1"
author: "Allison Li"
date: "04202025"
output: github_document
---

## Load Packages and Data

```{r load-packages, message=FALSE, warning=FALSE}
##install.packages("openintro")
library(tidyverse) 
library(tidymodels)
library(openintro)
```

## Exercise 1

```{r exercise1_code}
glimpse(evals)

##Distribution:
ggplot(evals, aes(x = score)) +
  geom_histogram(
    binwidth = 0.5, fill = "pink", color = "lightblue") +
  labs(title = "Distribution of Course Evaluation Scores", x = "Score", y = "Count")
```

This is a left skewed distribution, indicating that most students' average professor evaluation scores were relatively good (4-5, excellent). This is what I expected since I believe most professors are good at teaching classes, while very little students indicating neutral or negative attitudes towards their professions. 

## Exercise 2

```{r exercise2_code}

ggplot(evals, aes(x=bty_avg, y=score, color = "pink")) + 
  geom_point(alpha = .6) +
  labs(
    title = "Scatterplot of Professor Evaluation Score vs. Beauty Rating",
    x = "Average Beauty Rating",
    y = "Course Evaluation Score"
  )
```

According to the graph, most dotes clustered on lower average beauty rating and higher course evaluation scores. 
## Additional Exercises

*Repeat the format above for additional exercises.*

## Hint

For Exercise 12, the `relevel()` function can be helpful!
